R for Clinical Study Reports and Submission

### 2022-01-29 project-management.Rmd
Replace validation tracker image with kable

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("images/validation_tracker.png")
```

>>>>

```{r, echo=FALSE}
library("kableExtra")

df <- read.table("validation-tracker.tsv", stringsAsFactors = FALSE, header = FALSE, sep = "\t")

df %>%
  kbl(col.names = NULL) %>%
  kable_classic(full_width = FALSE, html_font = "'Times New Roman', Times, serif", font_size = 16) %>%
  add_header_above(
    c(
      "Program Name" = 1, "Program Validation Category" = 1,
      "Who" = 1, "Status" = 1, "Who" = 1, "Status" = 1, "Who" = 1, "Status" = 1
    ),
    line = FALSE,
    extra_css = "border: 1px solid #000;"
  ) %>%
  add_header_above(
    c(
      "<span></span>" = 2, "Requirement/Specification" = 2,
      "Developer Testing" = 2, "Independent Testing" = 2
    ),
    escape = FALSE,
    line = FALSE,
    extra_css = "border: 1px solid #000;"
  ) %>%
  column_spec(4, background = ifelse(df$V4 == "C", "#00ff00", "#ffff00")) %>%
  column_spec(6, background = ifelse(df$V6 == "C", "#00ff00", "#ffff00")) %>%
  column_spec(8, background = ifelse(df$V8 == "C", "#00ff00", "#ffff00")) %>%
  column_spec(1, extra_css = "border: 1px solid #000; text-align: left;") %>%
  column_spec(2:8, extra_css = "border: 1px solid #000; text-align: center;")
```

<p></p>
